Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-24 paper/paper.tex
halfway throw V.B.II

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the official
Test262~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}.\Comment{ This test suite contains
  87\% of all the tests we used.} We also considered test suites of
three of the four engines mentioned in
Section~\ref{sec:methodology:engines} and four other engines. Overall,
we selected a total of \totfiles{} JS
files. Table~\ref{tab:test-suites} shows the breakdown of tests we
considered. Column ``original'' shows the number of test cases for
each test suite. We did not consider tests from the \chakra{}
repository because they depend on non-portable objects. Notice that
the number of tests in \veight\ is low. That happens because \veight{}
uses many tests from Mozilla and \jsc{}; we discarded those to avoid
repetition and to give credit where it is due. The columns
``compile-in-all'' and ``no-fail-in-all'' correspond to the test files
used, respectively, in the test transplantaion experiment and the
differential testing experiment.

Column ``compile-in-all'' shows the number of test cases whose
execution does not throw errors because of an undefined variable or
property. We capture these cases by looking for the presence of
\CodeIn{ReferenceError} and \CodeIn{TypeError} in the output. A
\CodeIn{ReferenceError} (respectively, \CodeIn{TypeError}) is raised
when test execution attempts to access an undefined variable
(respectively, property of an object). We discarded those tests to
avoid noise in the experiments as they clearly indicate some missing
feature as opposed to bugs. For example, some tests use non-portable
names (\eg{}, \jsc{}'s \CodeIn{drainMicrotasks()} and \smonkey{}'s
\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
spec, not all engines currently support. We used the tests that lie
within the circle that appears in the table in the evaluation of test
transplantion, \ie{} the set ``compile-in-all'' minus set Test262. We
did not consider tests from the conformance suite as they are more
likely to indicate missing features as opposed to bugs. In addition,
engine developers have access to these test and are encouraged to run
them. Column ``no-fail-in-all'' shows the tests for which all engines
pass. This test set is used in the evaluation of differential
testing. Note that it is a proper subset of the ``compile-in-all''
test set. The tests from this group are used as fuzzing seeds. The
guarantee that they pass in all engines assures that, if discrepancies
occur, they are related to the changes in the input as opposed to the
original cause of failure.

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Number of test cases per
    suite. Column ``original'' shows the original size of the test
    suite, column ``compile-in-all'' shows the number of test cases
    for which engines do not throw compile error (\eg{}, undefined
    name), and column ``no-fail-all'' shows the number of test cases
    that pass in all four engines we analyzed.}
  \begin{tabular}{ccrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{3}{c}{\# JS files} \\
    \cline{3-5}
                               &         & original & compile-in-all &  no-fail-in-all \\
    \midrule
    TC-39 (Test262) & \cite{ecma262-conformance-suite} & 31,276 &
    29,846 & 17,639 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 &\marktopleft{c1} 1,021 & 955\\
    \smonkey\ & \cite{mozilla} & 2,634 & 2,116 & 1,686\\
    \veight{} & \cite{v8} & 75 & 57 & 57\\
    \midrule
    Duktape & \cite{duktape} & 1,195 & 921 & 915\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,878 & 1,837\\
    JSI & \cite{jsi} & 99 & 63 & 63\\
    Tiny-js & \cite{tinyjs} & 49 & 37\markbottomright{c1} & 37\\
    % \chakra{} & \cite{chakracore} & 2632 \\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule 
  \end{tabular}
\end{table}

@@

Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
1. RangeError: Offset is outside the bounds of the DataView
2. RangeError: byteOffset cannot be negative
3. RangeError: invalid or out-of-range index
  \end{lstlisting}
  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
    that led to a confirmed bug report in \chakra. The bug is caused
    by a required precondition check in the implementation of function
    \CodeIn{ToIndex} indirectly called by the test. }
\end{figure}

@@

Table~\ref{tab:cross-testing} shows the number of failures observed
for each pair of test suite and engine. The first column shows the
test suites and the first row shows the engines that run those
tests. We use a dash (``-'') to indicate that we did not consider the
combinations that associate a test suite with its parent engine;
failures in those cases would either indicate regressions or flaky
tests as opposed to unknown bugs for that engine. We did not run test
cases that fail on its parent engine in any other engine as that would indicate that
the test case could be broken. In total, 64 test cases
were discarded for that reason--6 from \jsc{} and 57 from
\smonkey. Furthermore, we required that a test does not manifest
compile errors as we want to focus on bugs in code not in tests. For
that reason, we used the tests listed under the column
``compile-in-all'' from Table~\ref{tab:test-suites}, totalling
\totalTestFilesCompileInAll{} cases. \Mar{can you confirm that we used
  ``compile-in-all'' and not ``origina'' as these numbers
  suggest?}\Fix{In total, 7,029 test files (\ie{}, 38369-31276-64)
  were considered in this experiment, which involved 24,922 test runs
  (\ie, (7029*4)-1021-57-2116).}  Of these, 812 failures were
manifested (3.25\% of the runs) across \textbf{543} distinct files
(7.72\% of the files). We observed from
the table that, considering this dataset, the Mozilla \smonkey\ was
the engine that failed the least whereas the Microsoft engine
\chakra\ failed the most. The \smonkey\ test suite also revealed more
failures than any other, as expected, considering that it is the suite
with more tests (see Table~\ref{tab:test-suites}).

>>>>

\subsection{Seed JS files\label{sec:seeds}}~
We selected test files from several public projects from GitHub. We
looked for self-contained tests from JS engine projects, initially
using the GitHub REST API~\cite{github-rest-api}. We noticed that some
of the tests we found depend on external libraries, which not all
engines we use support. We decided to discard those. For example, many
tests we found required a Node.js runtime~\cite{node} for
execution. The main source of test cases is the official
Test262~\cite{tc39-github} conformance test suite for the ECMA262
specification~\cite{ecmas262-spec}.\Comment{ This test suite contains
  87\% of all the tests we used.} We also considered test suites of
three of the four engines mentioned in
Section~\ref{sec:methodology:engines} and four other engines. Overall,
we selected a total of \totfiles{} JS
files. Table~\ref{tab:test-suites} shows the breakdown of tests we
considered. Column ``original'' shows the number of test cases for
each test suite. We did not consider tests from the \chakra{}
repository because they depend on non-portable objects. Notice that
the number of tests in \veight\ is low. That happens because \veight{}
uses many tests from Mozilla and \jsc{}; we discarded those to avoid
repetition and to give credit where it is due. The columns
``compile-in-all'' and ``no-fail-in-all'' indicate the tests used in
the test transplantaion experiment and the differential testing
experiment, respectively.

Column ``pass-in-par.'' shows the number of test cases that pass in
their parent engine. We discarded tests that fail in their parent
engine as we could not reliably indicate the reason for the failure,
so we assumed the test could be broken. We removed 63 test cases that
fail for that reason--6 tests from \jsc{} and 57 tests from
\smonkey. Column ``compile-in-all'' shows the number of test cases
whose executions do not throw errors because of an undefined variable
or property. We capture these cases by looking for the presence of
\CodeIn{ReferenceError} and \CodeIn{TypeError} in the output. A
\CodeIn{ReferenceError} (respectively, \CodeIn{TypeError}) is raised
when test execution attempts to access an undefined variable
(respectively, property of an object). We discarded those tests to
avoid noise in the experiments as they clearly indicate some missing
feature as opposed to bugs. For example, some tests use non-portable
names (\eg{}, \jsc{}'s \CodeIn{drainMicrotasks()} and \smonkey{}'s
\CodeIn{Error.lineNumber}) or use functions that, albeit part of the
spec, not all engines currently support. We used the
\totalTestFilesForTestTransplantation{} tests included in the circle
from the table in the evaluation of test transplantion, \ie{}, the
difference between sets ``compile-in-all'' and Test262. We did not
consider tests from the conformance suite as they are more likely to
indicate missing features as opposed to bugs. In addition, engine
developers have access to these test and are encouraged to run
them. Column ``no-fail-in-all'' shows the tests for which all engines
pass. This test set is used in the evaluation of differential
testing. Note that it is a proper subset of the ``compile-in-all''
test set. The tests from this group are used as fuzzing seeds. The
guarantee that they pass in all engines assures that, if discrepancies
occur, they are related to the changes in the input as opposed to the
original cause of failure.

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Number of test cases per
    suite. Column ``original'' shows the original size of the test
    suite, column ``compile-in-all'' shows the number of test cases
    for which engines do not throw compile error (\eg{}, undefined
    name), and column ``no-fail-all'' shows the number of test cases
    that pass in all four engines we analyzed.}
  \setlength{\tabcolsep}{2.5pt}      
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & original & pass-in-par. & compile-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & 31,276 & - &  29,846 & 17,639 \\
    \midrule
    \jsc{} & \cite{webkit} & 1,031 & 1,025 &\marktopleft{c1}1,021 & 955\\
    \smonkey\ & \cite{mozilla} & 2,634 & 1,977 & 2,116 & 1,686\\
    \veight{} & \cite{v8} & 75 & 75 & 57 & 57\\
    \midrule
    Duktape & \cite{duktape} & 1,195 & 1,195 & 921 & 915\\ 
    \jerry{} & \cite{jerryscript} & 1,951 & 1,951 & 1,878 & 1,837\\
    JSI & \cite{jsi} & 99 & 99 & 63 & 63\\
    Tiny-js & \cite{tinyjs} & 49 & 49 & 37\markbottomright{c1} & 37\\
    \midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule 
  \end{tabular}
\end{table}

@@

Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
1. RangeError: Offset is outside the bounds of the DataView
2. RangeError: byteOffset cannot be negative
3. RangeError: invalid or out-of-range index
  \end{lstlisting}
  \caption{\label{fig:lo-truepositive}Example of a ``\lo'' warning
    that led to a confirmed bug report in \chakra. The bug is caused
    by a required precondition check in the implementation of function
    \CodeIn{ToIndex}~\cite{ecmas262-getviewvalue}, which is indirectly called by the test. }
\end{figure}

@@

Table~\ref{tab:cross-testing} shows the number of failures observed
for each pair of test suite and engine. The first column shows the
test suites and the first row shows the engines that run those
tests. We use a dash (``-'') to indicate that we did not consider the
combinations that associate a test suite with its parent engine;
failures in those cases would either indicate regressions or flaky
tests as opposed to unknown bugs for that engine. As explained in
Section~\ref{sec:seeds}, we used in this experiment the
\totalTestFilesForTestTransplantation{} tests included in the circle
from Table~\ref{tab:test-suites}. Running those tests we observed a
total of 812 failures manifested across 543 distinct files (8.9\% of
total). Table~\ref{tab:cross-testing} shows that, considering the
engines analyzed, \smonkey\ was the engine that failed the least
whereas \chakra\ was the engine that failed the most. The
\smonkey\ test suite also revealed more failures than any other,
perhaps as expected, considering that it is the suite with more tests
(see Table~\ref{tab:test-suites}).
